# Reproducible Research: Peer Assessment 1

setwd('~/Desktop/coursera/data specialization/5.Reproducible Research/project1/')
## Loading and preprocessing the data
```{r}
data <- read.csv("activity.csv", colClasses = c("numeric", "Date", "numeric"))
````

## What is mean total number of steps taken per day?
### Make a histogram of the total number of steps taken each day
```{r}
split <- split(data, data$date)
total_steps <- sapply(X=split, FUN=function(x) sum(na.omit(x$steps)))
library(lattice)
histogram(total_steps)
````
### Calculate and report the **mean** and **median** total number of steps taken per day
```{r}
steps <- sapply(X=split, FUN=function(x) sum(na.omit(x$steps)))
mean <- mean(steps, na.rm=TRUE)
median <- median(steps, na.rm=TRUE)
````
The mean is `r mean` and the median is `r median`.
## What is the average daily activity pattern?
1. Make a time series plot (i.e. `type = "l"`) of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
Sorry I couldn't finished on time
```{r}

max_num_steps <- which(data2 == max(na.omit(data2$steps)))
max_num_steps
data2[max_num_steps,]
````
## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
